Make data files

### 2021-11-27 make_data.Rmd
Standings and division mapping

@@

```{r graphlist}
graphlist <- lapply(
  sort(unique(trades$season)),
  function(s) {
    g <- graph_from_data_frame( 
      edb %>%
        filter(season == s) %>%
        select(P1, P2), 
      directed=FALSE)
    E(g)$weight <- count_multiple(g)
    g <- simplify(g)
    g$season <- s
    g
  }
)
```

@@

```{r graphlist-save}
saveRDS(graphlist, file = "wgl.rds")
```

>>>>

# Divisions

From data on standings

```{r}
divisions <- readRDS(here::here("data", "standings.rds")) %>%
  distinct(
    season_from,
    division = purrr::map_chr(strsplit(division, " "), 1),
    team_acronym = purrr::map_chr(strsplit(full_team_name, " "), tail, 1)
  )
```

@@

```{r graphlist}
graphlist <- lapply(
  sort(unique(trades$season_from)),
  function(s) {
    # Select trades
    e <- trades %>%
      filter(season_from == s) %>%
      select(P1, P2)
    # Nodes
    n <- data.frame(
      name = sort(unique(c(e$P1, e$P2)))
    ) %>%
      left_join(
        divisions %>%
          filter(season_from == s) %>%
          rename(div = division),
        by = c("name" = "team_acronym")
      )
    g <- graph_from_data_frame(e, vertices = n, directed=FALSE)
    E(g)$weight <- count_multiple(g)
    g <- simplify(g)
    g$season <- paste0(s, "-", s+1)
    g
  }
)
```

@@

```{r graphlist-save}
saveRDS(graphlist, file = here::here("data", "wgl.rds"))
```
